Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-10 arxiv/setup.tex

\paragraph{Organizations.}
The rest of this paper is organized as follows.
In Section \ref{sec_prelim}, we describe and random matrices. We describe several well-known facts.
In Section \ref{sec_example}, we describe illustrative examples of our technical results and discuss their implications.
In Section \ref{sec_same}, we consider the same covariates setting and show the generalization error of hard parameter sharing.
In Section \ref{sec_diff}, we consider the different covariates setting and show the bias and variance asymptotics using random matrix theory.

\paragraph{Notations.}
Let $B^\star \define [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}] \in \real^{p\times t}$ denote the ground truth model parameters.
Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.
Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.
We shall say an event $\Xi$ holds with high probability (w.h.p.) if $\P(\Xi)$ goes to $1$ as $p$ goes to infinity.
%, while we say $\Xi$ holds with overwhelming probability (w.o.p.) if for any large constant $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
We shall refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices following the standard notations in high-dimensional statistics.

>>>>

\smallskip
\noindent\textbf{Organizations.}
The rest of this paper is organized as follows.
In Section \ref{sec_same}, we present the bias-variance decomposition for hard parameter sharing.
In Section \ref{sec_diff}, we present our technical results for showing how varying sample sizes and covariate shifts impact hard parameter sharing using random matrix theory.
In Section \ref{sec_exp}, we validate our theory in both simulations and a real world classification task.
In Section \ref{sec_conclude}, we conclude the paper and describe several open questions.

\paragraph{Notations.}
Let $B^\star \define [{\beta}_1,{\beta}_2,\dots,{\beta}_{t}] \in \real^{p\times t}$ denote the ground truth model parameters.
Let $\cE \define [\varepsilon_1, \varepsilon_2, \dots, \varepsilon_t] \in \real^{n \times t}$ denote the random noise.
Let $Y$ denote $[Y^{(1)}, Y^{(2)}, \dots, Y^{(t)}]$.
We can also write $Y = XB^{\star} + \cE$.
Let $A = [A_1, A_2, \dots, A_t] \in \real^{r\times t}$ be a matrix notation that contains all the output layer parameters.
We shall use $\oo(1)$ to mean a small positive quantity that converges to 0 as $p$ goes to infinity.
We shall say an event $\Xi$ holds with high probability (w.h.p.) if $\P(\Xi)$ goes to $1$ as $p$ goes to infinity.
%, while we say $\Xi$ holds with overwhelming probability (w.o.p.) if for any large constant $D>0$, $\P(\Xi)\ge 1- p^{-D}$ for large enough $p$.
For a matrix $X$, let $\lambda_{\min}(X)$ denote its smallest singular value and $\norm{X}$ denote its spectral norm.
Let $X^+$ denote its Moore-Penrose psuedoinverse.
We shall refer to random matrices of the form $\frac {X^\top X} n$ as sample covariance matrices following the standard notations in high-dimensional statistics.
